What is the Effect of X on Y?

### 2021-09-07 latex-slides/slides.tex
Update slides template

% Title --------------------------------------------
\title{Title}
\subtitle{Subtitle}
\date{\today}
\author{Kyle Butts}
% \institue{}

@@

% ------------------------------------------------------------------------------
\maketitle
% ------------------------------------------------------------------------------

@@

\begin{frame}{Components}{Colors}
    {\color{navy} Test sentence with \textbackslash color\{navy\}}\newline
    {\color{kelly} Test sentence with \textbackslash color\{kelly\}}\newline
    {\color{ruby} Test sentence with \textbackslash color\{ruby\}}\newline
    {\color{alice} Test sentence with \textbackslash color\{alice\}}\newline
    {\color{daisy} Test sentence with \textbackslash color\{daisy\}}\newline
    {\color{coral} Test sentence with \textbackslash color\{coral\}}\newline
    {\color{jet} Test sentence with \textbackslash color\{jet\}}\newline
    {\color{asher} Test sentence with \textbackslash color\{asher\}}\newline
\end{frame}

\begin{frame}{Components}{Two Columns general}
    \begin{columns}[T] % T = vertical align columns at the top
    \begin{column}{.50\textwidth}
        {\color{accent}\rule{\linewidth}{2pt}}
        Column 1

        \begin{enumerate}
            \item Bullet points for this column that can go over lines
            \item b
            \item c
        \end{enumerate}
    \end{column}

@@

        \begin{enumerate}
            \item a
            \item b
            \item c
        \end{enumerate}
    \end{column}
    \end{columns}
\end{frame}

\begin{frame}{Components}{Example of tikz figure}

\begin{figure}
\begin{center}
\begin{tikzpicture}[node distance=1.5cm]
    % nodes %
    \node[text centered] (d) {$D$};
    \node[below right of = d, text centered] (x) [draw, shape=circle, line width = 1] {$X$};
    \node[above right of = x, text centered] (y) {$Y$};
    \node[below of = x, text centered, purple] (z) {$Z$};

    % edges %
    \path[->, line width= 1] 
        (d) edge (y)
        (x) edge (d)
        (x) edge (y);
    \path[->, line width= 1, purple]
        (z) edge [out=135, in=260, looseness=0.5] node[left, black] {$\text{Good variation in D}$} (d)
        (z) edge [out=45, in=280, looseness=0.5] (y);
\end{tikzpicture}
\end{center}
\end{figure}

\end{frame}

@@

    \begin{adjustbox}{max width = \textwidth, width = 0.75\textwidth, center}
        \begin{threeparttable}
            \begin{tabular}{@{} lcc @{}} 
                \toprule
                & \multicolumn{2}{c}{\textit{Dependent variable: Overall Rating}} \\ 
                \cline{2-3} \\
                & (1) & (2)\\ 
                \midrule

                \marktopleft{ex1}Handling of Complaints & 0.692$^{***}$ (0.149) & 0.682$^{***}$ (0.129) \markbottomright{ex1} \\ 
                No Special Privileges & $-$0.104 (0.135) & $-$0.103 (0.129)  \\ 
                Opportunity to Learn & 0.249 (0.160) & 0.238$^{*}$ (0.139) \\ 
                Performance-Based Raises & $-$0.033 (0.202) &  \\ 
                Too Critical & 0.015 (0.147) &  \\ 
                Advancement & 11.011 (11.704) & 11.258 (7.318) \\ 
                \hline \\[-1.8ex] 
                Observations & 30 & 30 \\ 
                R$^{2}$ & 0.715 & 0.715 \\ 
                \bottomrule

            \end{tabular} 
            % Notes 
            \begin{tablenotes}
                \item \textit{Notes.} $^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01.
            \end{tablenotes}
        \end{threeparttable}
    \end{adjustbox}
\end{table}
\end{frame}

@@

>>>>

% Title --------------------------------------------
\title{What is the Effect of X on Y?}
\subtitle{Evidence from a Personal Anecdote}
\date{\today}
\author{Kyle Butts}

@@

% ------------------------------------------------------------------------------
\begin{frame}
\maketitle

% \vspace{2.5mm}
% {\footnotesize $^*$ A bit of extra info here. Add an asterich to title or author}
\end{frame}
% ------------------------------------------------------------------------------

@@

\begin{frame}{Components}{Colors}
    {\color{navy} Test sentence with \textbackslash color\{navy\}}\newline
    {\color{purple} Test sentence with \textbackslash color\{purple\}}\newline
    {\color{kelly} Test sentence with \textbackslash color\{kelly\}}\newline
    {\color{ruby} Test sentence with \textbackslash color\{ruby\}}\newline
    {\color{alice} Test sentence with \textbackslash color\{alice\}}\newline
    {\color{daisy} Test sentence with \textbackslash color\{daisy\}}\newline
    {\color{coral} Test sentence with \textbackslash color\{coral\}}\newline
    {\color{cranberry} Test sentence with \textbackslash color\{cranbery\}}\newline
    {\color{slate} Test sentence with \textbackslash color\{slate\}}\newline
    {\color{jet} Test sentence with \textbackslash color\{jet\}}\newline
    {\color{asher} Test sentence with \textbackslash color\{asher\}}\newline
\end{frame}

\begin{frame}{Components}{Two Columns}
    \begin{columns}[T]
    \vspace{0pt}
    \begin{column}{.50\textwidth}
        \vspace{0pt}
        {\color{accent}\rule{\linewidth}{2pt}}
        Column 1

        \begin{enumerate}
            \item Bullet points for this column that can go over lines
            \item b
            \item c
        \end{enumerate}

        \vspace*{50mm} % Ensures columns are up top; delete if you want columns centered on page
    \end{column}

@@

        \begin{itemize}
            \item a
            \item b
            \item c
        \end{itemize}
    \end{column}
    \end{columns}
\end{frame}

\begin{frame}{Components}{Two Columns with Figure}
    \begin{columns}[T]
    \vspace{0pt}
    \begin{column}{.60\textwidth}
        \includegraphics[width=\textwidth]{img/kanagawa.jpg}

        \vspace*{50mm} % Ensures columns are up top; delete if you want columns centered on page
    \end{column}

    \begin{column}{.40\textwidth}
        \begin{itemize}
            \item A point about the figure that is potentially important.
            \item Another point about the figure that is also potentially important.
        \end{itemize}
    \end{column}
    \end{columns}
\end{frame}

@@

    \begin{adjustbox}{max width = \textwidth, width = 0.5\textwidth, center}
        \begin{threeparttable}
            \begin{tabular}{@{} l *{2}{r} @{}} 
                \toprule
                & \multicolumn{2}{c}{\textit{Dependent variable: Overall Rating}} \\ 
                \cline{2-3} \\
                & (1) & (2)\\ 
                \midrule

                \only<1>{
                    Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
                    &  (0.149) & (0.129) \\
                }
                \only<2>{
                    \marktopleft{ex1}Handling of Complaints & 0.692$^{***}$& 0.682$^{***}$ \\ 
                    &  (0.149) & (0.129) \markbottomright{ex1} \\
                }
                No Special Privileges & -0.104 & $-$0.103  \\ 
                & (0.135) & (0.129) \\
                Opportunity to Learn & 0.249 & 0.238$^{*}$ \\ 
                & (0.160) & (0.139) \\
                Performance-Based Raises & -0.033 &  \\ 
                & (0.202) & \\
                Too Critical & 0.015 &  \\ 
                & (0.147) & \\
                Advancement & 11.011 & 11.258 \\ 
                & (11.704) & (7.318) \\

                \midrule 
                Observations & 30 & 30 \\ 
                R$^{2}$ & 0.715 & 0.715 \\ 
                \bottomrule

            \end{tabular} 
            % Notes 
            \begin{tablenotes}
                \item \textit{Notes.} $^{*} p<0.1$; $^{**} p<0.05$; $^{***} p<0.01$.
            \end{tablenotes}
        \end{threeparttable}
    \end{adjustbox}
\end{table}

{\small
Use \textbackslash marktopleft\{name\} and \textbackslash markbottomright\{name\} to create box.
}
\end{frame}

@@

\begin{frame}{Figure}{Full-size Figures}
    You can use the command \textbackslash imageframe\{img-path\} and it will create a full-frame of a picture.

    \begin{itemize}
        \item Ideally, your figure is the same aspect as the frame $4:3$ or $16:9$ or else there will be white space in one of the directions.
    \end{itemize}
\end{frame}
